\documentclass[12pt]{article}

\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%%
         %\begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
         %\vspace{-0.6in}
         	\begin{center}
                {\underline{\bfseries #1}}\\%[-0.15\baselineskip]%
                 %\rule{\columnwidth}{1pt}%
                 \end{center}
         %\end{minipage}
         }

\newcommand{\makesection}[1]{\underline{\bfseries #1:}}

\usepackage{pslatex}
\setlength{\parindent}{0in}

\usepackage[top=0.5in,left=1.0in,bottom=1.0in,right=1.0in]{geometry}

\begin{document}

\makeheading{Nicholas Penha Malaya}

\makesection{Education}
\begin{itemize}
\item PhD, Engineering, The University of Texas at Austin, 2016
\item M.S., Engineering, The University of Texas at Austin, 2009
\item B.S., Physics \& Mathematics, Georgetown University, 2007
\end{itemize}

\makesection{Research Experience}
\begin{itemize}
\item Member of the Technical Staff, AMD Research, 2016-present
\item Researcher, UT:Austin, Institute for Computational Engineering and Sciences, 2010-2014
\item Assistant Researcher, National Institute of Standards \& Technology, 2005
\end{itemize}

\makesection{Current membership in professional organizations}
\begin{itemize}
\item Member, Association for Computing Machinery (ACM)
\item Member, Society of Industrial and Applied Mathematics (SIAM)
\item Member, American Institute of Aeronautics and Astronautics (AIAA)
\end{itemize}

\makesection{Honors and Awards:}
\begin{itemize}
\item ``Best Student Paper Finalist'' -- SC13, Denver, CO	  
\item ``Best Paper" - 2012 TACC-Intel Highly Parallel Computing Symposium, Austin, TX
\item Cockrell School of Engineering Thrust 2000 Ph.D. Fellowship
\item 2007 Treado Medal, Georgetown University
\end{itemize}

\makesection{Service Activities}

\begin{itemize}
 \item Industry Mentor, RIPS IPAM UCLA, 2017-Present
 \item Program Committee Member, SciPy 2017-Present
 \item Program Committee Member, PEARC17
 \item Program Committee, Great Lakes Consortium for Petascale Computation (2012--2015)
 \item Reviewer, Blue Waters Graduate Fellowship Program (2014--present)
\item Journal referee: Parallel Computing, Journal of Fluid Mechanics, Engineering with Computers, Journal of Computational Physics
\item Program Committee, Great Lakes Consortium for Petascale Computation (2012--present)
\item Reviewer, Blue Waters Graduate Fellowship Program (2014--present)
\end{itemize}

\makesection{Five most relevant publications}
\begin{itemize}
\item Gerber, Patrik, et al. "Solving OpenAI’s Car Racing Environment with
Deep Reinforcement Learning and Dropout." arXiv preprint (2019)
\item Li, Zhaoqi, et al. "Exploration of Numerical Precision in Deep Neural Networks." arXiv preprint arXiv:1805.01078 (2018).
\item \textbf{Nicholas Malaya}, Shuai Che, Joseph L. Greathouse, René van Oostrum,
Michael J. Schulte, Accelerating Matrix Processing with GPUs
Published in the Proceedings of the 24th IEEE Symposium on Computer
Arithmetic (ARITH 24), July, 2017 
\item McMahan J.A., et al., A Linear Regression
Framework for the Verification of Bayesian Model Calibration
Algorithms. ASME. J. Verif. Valid. Uncert. 2017. doi:10.1115/1.4037705. 
\item T. A. Oliver, \textbf{N. Malaya}, R. Ulerich, and R. D. Moser, “Estimating
Uncertainties in Statistics Computed from DNS,”
Phys. Fluids 26, 035101 (2014). http://dx.doi.org/10.1063/1.4866813 
\end{itemize}

\makesection{Five secondary publications}
\begin{itemize}
\item M. Lee, \textbf{N. Malaya}, and R. D. Moser, ``Petascale direct numerical simulation of turbulent channel flow on up to 786k cores,'' in Proceedings 
of the 2013 ACM/IEEE International Conference for High Performance
Computing, Networking, Storage and Analysis (SC). ACM Press, 2013 {\bf(Best
Student Paper Finalist)}
\item Damon McDougall, \textbf{Nicholas Malaya}, Robert D. Moser, ``The Parallel C++
Statistical Library for Bayesian Inference: QUESO'', Handbook of
Uncertainty Quantification, edited by Roger Ghanem, David Higdon, Houman
Owhadi, (Springer International Publishing, 2017) 
\item Schulz, Karl W., et al. ``Early experiences porting scientific applications to the Many Integrated Core (MIC) platform.'' TACC-Intel Highly Parallel Computing Symposium, Austin, Texas. Vol. 44. 2012.
\item \textbf{N Malaya}, D McDougall, C Michoski, M Lee, CS Simmons,
Experiences Porting Scientific Applications to the Intel (KNL) Xeon Phi Platform
Proceedings of the Practice and Experience in Advanced Research Computing
2017 on Sustainability, Success and Impact
\item \textbf{N. Malaya}, K. C. Estacio-Hiroms, R. H. Stogner, K. W. Schulz, P. T. Bauman,
G. F. Carey, ``MASA: A Library for Verification Using Manufactured and Analytical Solutions'',
Engineering with Computers, 29(4), 487--496, 2013
\end{itemize}

\end{document}
