
\textbf{Nicholas Malaya}, ``Enabling Portable Directive-Based Programming at Exascale'', WACCPD, SC20, November 13th, 2020. 

\blankline

\textbf{Nicholas Malaya}, ``Hardware and Software Co-design: Preparing and Optimizing Scientific Applications for Exascale Computing'', Institute for Applied Computational Science, Harvard University
		 February, 21st, 2020. 

\blankline

\textbf{Nicholas Malaya}, ``AMD EPYC CPUs and Radeon Instinct GPUs for HPC'', El Capitan Application Readiness Kick-off Workshop, Lawrence Livermore National Laboratory, 
		 January 14th, 2020. 

\blankline

\textbf{Nicholas Malaya}, ``AMD EPYC CPUs and Radeon Instinct GPUs for HPC'', El Capitan Application Readiness Kick-off Workshop, Sandia National Laboraties, 
		 Dec. 3rd, 2019. 

\blankline

\textbf{Nicholas Malaya}, ``AMD GPU Evolution'', Frontier Application Readiness Kick-off Workshop, Oak Ridge Leadership Computing Facility, 
		 Oct. 8th, 2019. 

\blankline

\textbf{Nicholas Malaya, Max Kiehn}, ``Automated Software Testing with Machine Learning'', AMD Software Tech Forum, 
		 September 9th, 2019. 

\blankline

\textbf{Nicholas Malaya}, ``Learning Systems'', Department of Computer Science, 
		 University of Chicago, November 28th, 2018. 

\blankline

\textbf{Nicholas Malaya}, ``Full-Stack Open-Source Supercomputing'', OpenSuCo4 Keynote at SC18
		 Dallas, TX, November 12th, 2018. 

\blankline


\textbf{Nicholas Malaya}, ``Technology Directions in AI'', UT McCombs School of Business, 
		 Austin, TX, October 9th, 2018. 

\blankline

\textbf{Nicholas Malaya}, ``Numerical Investigation of Synthetic Dust Devils'', AMD Research, 
		 Austin, TX, July 8th, 2016. 

\blankline

\textbf{Nicholas Malaya}, ``Introduction to Scientific Computation'', Dell HPC Innovation Lab, 
		 Austin, TX, September 2nd, 2016. 

\blankline

\textbf{Nicholas Malaya}, ``Verification, Validation and Uncertainty Quantification in Turbulence Simulations'', Texas Advanced Computing Center, 
		 Austin, TX, May 12th, 2016. 

\blankline

\textbf{Nicholas Malaya}, ``Numerical Investigation of Synthetic, Buoyancy-Induced Columnar Vortices'', Sandia National Laboratories, 
		 Albuquerque, NM, March 16th, 2016. 

\blankline

\textbf{Nicholas Malaya}, ``Verification \& Software Quality in Scientific
      Computing'', Los Alamos Computational Physics Student Summer
      Workshop, 2014. 

\blankline

\textbf{Nicholas Malaya}, ``The Method of Manufactured Solutions'', Los Alamos
      Computational Physics Student Summer Workshop, 2013.

\blankline

\textbf{Nicholas Malaya}, Christopher Simmons, ``Scientific Software Engineering
      Best Practices'', Los Alamos Computational Physics Student Summer
      Workshop, 2012.

\blankline

\textbf{Nicholas Malaya} \& Robert D. Moser, ``Tools and Techniques for Code
Verification using Manufactured Solutions.'', SIAM Conference on
Uncertainty Quantification, April 2-4, 2012, Raleigh, North Carolina 

\blankline

\textbf{Nicholas Malaya}, Karl W. Schulz, ``Verification through the MASA
      Library'', Los Alamos Computational Physics Student Summer
      Workshop, 2011.

\blankline

\textbf{Nicholas Malaya}, Rhys Ulerich, Robert Moser, ``Petascale Direct
Numerical Simulations of Turbulent Channel Flow'', ESP Kick-off
Workshop and Project Plan Presentation, Oct. 18th, 2010.

\blankline

\textbf{Nicholas Malaya}``Theoretically Based Optimal LES'', TFS/NRE
Seminar, Department of Mechanical Engineering, Oct. 29th, 2009. 


