%
%\begin{outerlist}
%\item [1.]

McMahan JA, Williams BJ, Smith RC, \textbf{Malaya N.}, A Linear Regression
Framework for the Verification of Bayesian Model Calibration
Algorithms. ASME. J. Verif. Valid. Uncert. 2017. doi:10.1115/1.4037705. 

\blankline

 Graham, J., Kanov, K., Yang X.I.A., Lee M.K., \textbf{Malaya, N.}, 
Lalescu, C.C., Burns, R., Eyink, G., Szalay, A., Moser, R.D. \& 
Meneveau, C. ``A Web Services-accessible database of turbulent channel
flow and its use for testing a new integral wall model for LES.''Journal
of Turbulence  (2015)

\blankline

M. Lee, \textbf{N. Malaya}, Rhys Ulerich, Robert D. Moser,  “Experiences from
Leadership Computing in Simulations of Turbulent Fluid Flows,”
Computing in Science \& Eng., vol. 16, no. 5, 2014, pp. 24–31.

\blankline

T. A. Oliver, \textbf{N. Malaya}, R. Ulerich, and R. D. Moser, “Estimating
uncertainties in statistics computed from direct numerical simulation,”
Phys. Fluids 26, 035101 (2014). http://dx.doi.org/10.1063/1.4866813 

\blankline

M. Lee, \textbf{N. Malaya}, and R. D. Moser, ``Petascale direct numerical sim-
ulation of turbulent channel flow on up to 786k cores,'' in Proceedings
of the 2013 ACM/IEEE International Conference for High Performance
Computing, Networking, Storage and Analysis (SC). ACM Press, 2013 {\bf(Best
Student Paper Finalist)}

\blankline

\textbf{N. Malaya}, K. C. Estacio-Hiroms, R. H. Stogner, K. W. Schulz, P. T. Bauman,
G. F. Carey, ``MASA: A Library for Verification Using Manufactured and
Analytical Solutions", Engineering with Computers, 29(4), 487--496, 2013

\blankline

\textbf{N. Malaya}, T. Oliver, K. C. Estacio-Hiroms, ``Manufactured Solutions for
the Favre-Averaged Navier-Stokes Equations 
with Eddy-Viscosity Turbulence Models'', Technical Paper, 50th AIAA ASM, 2012.

\blankline

\textbf{Nicholas Malaya}, Karl W. Schulz, Robert D. Moser
``Petascale I/O using HDF-5'', Teragrid'10 Technical Paper, Association for Computing Machinery,
August 2, 2010.

\blankline

Robert D. Moser, \textbf{Nicholas P. Malaya}, Henry Chang, et. al.,
``Theoretically based optimal large-eddy simulations'', Physics of Fluids, October 23, 2009.

%==================================================================
% END OF FILE
%==================================================================